### 2021-03-14 manuscript.tex
most of the paper

\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\title{CaRSA Data Identify, Collect, and Connect: A second-generation, national GeoLD system in Australia}
\titlerunning{CaRSA LocI}

\author{
    Nicholas J. Car\inst{1}\orcidID{0000-0002-8742-7730} \and \\
    Irina Bastrakova\inst{2}
}

\authorrunning{Car N.J. et al.}

\institute{
    {
    SURROUND Australia Pty Ltd., Australia \&\\
    Australian National University, Australia\\
    \email{nicholas.car@surroundaustralia.com}
    %\url{https://surroundaustralia.com}
    }
    \and
    {
        Geoscience Australia\\
        \email{irina.bastrakova@ga.gov.au}
    }
}

\maketitle

\begin{abstract}
In 2018 – 2020, Australia built two \textit{Linked Data} ``spines'' - themed collections of interoperable reference data - called LocI and LongSpine. 
LocI (Location Index) consists of 7 nationally-significant spatial datasets such as the Australian Statistical Geographies System. 
LongSpine (Longitudinal Spine of Government Functions) consists of multiple datasets of Australian government structure, such as the 
Australian Government Organisations Register, as well as vocabularies of government functions. Both projects interpreted existing open 
datasets into Linked Data form and provided online delivery of their the parts as well as infrastructure for their use as a single system.\\

Here described is the Climate and Resilience Services Australia’s Data Identify, Collect and Connect project's next-generation 
implementation of the ``spines'' patterns and architecture and partial direct reuse of LocI. We discuss: differences with the originals, in particular LocI; original 
element reuse; and future-proofing steps, technical and non-technical. We also discuss the new expectations placed on this second-generation 
system, in particular the requirement to work with non-Linked Data spatial data systems, and how this system 
is pushing spatial and \textit{Semantic Web} standards development such as DGGS and GeoSPARQL.

\keywords{Location Index \and LocI \and LongSpine \and GeoSPARQL \and DGGS \and Spatial Data on the Web \and Australia \and data spine \and national data infrastructure}
\end{abstract}

\section{Introduction}\label{sec:introduction}
\subsection{CaRSA Motivation}
Climate and Resilience Services Australia (CaRSA) is a new Australia government cross-agency initiative\footnote{``Australia commits to climate resilience'', \url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}
that will:

\begin{quote}
    connect and leverage the Commonwealth’s extensive climate and natural disaster risk information to further prepare for and build 
    resilience to natural disasters
\end{quote}

Since Australia is prone to very damaging natural disasters such as bush fires, floods and droughts, this is a major government initiative
allocated good resourcing and the commitment is for multiple years.

\subsection{CaRSA Demonstrator Projects}
Several of the demonstrator projects for CaRSA sought to test different ways of combining information from multiple government agencies 
relevant to natural disaster management. Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
standardiseing web service-delivered information and cross-cataloging datasets, but forward-looking methdos are too. In particular,
\textit{Semantic Web} (SW) and \textit{Linked Data} (LD) technologies\footnote{By ``Linked Data'', as opposed to ``linked data'' or ``data linkage'' etc.,
we mean systems and data that implement a number of \textit{Semantic Web} technologies (RDF, OWL, SKOS, SPARQL, etc.) which are primarily 
defined as a series of \href{https://www.w3.org/standards/semanticweb/data}{World Wide Web Consortium} (W3C) standards. The W3C's defintion of 
\textit{Semantic Web} is that it is a ``Web of Data'', an evolved Internet able to be queried by machineswhich can draw inferences from it.}
are being used to integrate different, but relativley similar, datasets that are published in a distributed manner and
\textit{Discrete Global Grid System} (DGGS) spatial data methods are being used to integrate spatial data from multiple sources.

This paper describes the SW/LD and DGGS approaches being implemented in CaRSA's ``Data Identify, Collect, and Connect'' project that we will 
refere to as \textit{the project}. The project extends the approach taken by the Location Index project described in the next section.

\section{LocI: The Loction Index}\label{sec:loci}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{images/loci-brochure.png}
    \caption{A project brochure image, from \cite{car_location_2019}, of LocI with respect to
    Australian government \textit{Environment}, \textit{Society} and \textit{Economy} data}
    \label{fig:geosparql11ontology}
\end{figure}

In 2018 - 2020, Australian spatial data and research agencies implemented a:

\begin{quotation}
    national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}
\end{quotation}

This system, known as the Location Index (LocI)~\cite{car_location_2019}, aims to ``better geospatially integrate and analyze data across 
government portfolios and information domains''. The main use case addressed by LocI's is to greatly reduce the time taken by government 
workers in data analysis using spatial information by providing pre-integrated, authoratitive, spatial datasets that can be used in 
online, open data scenarios, within secure data integration environments and across the two.

Some of the interesting aspects of LocI's design include:

\begin{itemize}
    \item[$\ast$] federated publication of datasets via standard Linked Data APIs
    \item[$\ast$] use of VoID \texttt{Linkset}~\cite{alexander_describing_2011} instances to crosswalk datasets
    \begin{itemize}
        \item[$-$] these are independently-selectable for use meaning that a specific ccrosswalk, of potentially many, may be selected for use
    \end{itemize} 
    \item[$\ast$] use of a \textit{Geometry Data Service}\footnote{The service is online at \url{https://gds.loci.cat/}} for spatial integration
    \begin{itemize}
        \item[$-$] this service extends common use of using GeoSPARQL~\cite{open2012ogc} by storing \texttt{Geometry} instances seperately from the \texttt{Feature} instances they are the geometries for. This allows the geometry data to be managed in a PostGIS database~\footnote{\url{https://postgis.net/}}, not a triplestore, as usually used for GeoSPARQL data.
    \end{itemize}
    \item[$\ast$] several different clients for different uses
    \begin{itemize}
        \item[$-$] such as \textit{Excelerator}\footnote{\url{https://loci.cat/excelerator.html}}, used to upload data according to one spatial reference system and download it reapportioned according to another
    \end{itemize}
\end{itemize}

LocI's initial spatial datasets are from a number of domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
\footnote{The original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by LocI: \url{http://linked.data.gov.au/dataset/geofabric}}, 
a collection of surface hydrology features), human/census (the \textit{Australian Statistical Geography Standard} spatial areas)
\footnote{Non-RDF dataset: \url{https://geo.abs.gov.au/arcgis/services/ASGS2016/MB/MapServer/WFSServer}, LD version: \url{http://linked.data.gov.au/dataset/asgs2016}}, 
and cartographic/administrative (the \textit{National Composite Gazetteer of Australia})\footnote{LD version: \url{https://linked.data.gov.au/dataset/placenames}}.

The LocI system's architecture is shown in \ref{fig:loci-arch} for architectural details. It shows the LocI Data Cache, which is a multi-graph triplestore, 
obtains its data by ``pulling'' RDF datasets through APIs that both interpret non-RDF data for online delivery and are also able to create static RDF 
versions of the datasets. All LocI datasets conform to the LocI Ontology\footnote{\url{http://linked.data.gov.au/def/loci}} which imports the GeoSPARQL
\footnote{\url{http://www.opengis.net/doc/IS/geosparql/1.0}} and DCAT\footnote{\url{https://www.w3.org/TR/2014/REC-vocab-dcat-20140116/}} ontologies. 
Alongside the Cache is a traditional spatial DB - PostGIS\footnote{\url{https://postgis.net/}} used to perform fast geometry intersections.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{images/loci-arch.png}
    \caption{An informal architecture diagram of the LocI project's \textit{Linked Data} infrastructure.}
    \label{fig:loci-arch}
\end{figure}

\section{CaRSA Project Changes}\label{sec:changes}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{images/carsa-arch.png}
    \caption{An informal architecture diagram of the CaRSA project's \textit{Linked Data} infrastructure}
    \label{fig:geosparql11ontology}
\end{figure}

\section{Conclusions}\label{sec:conclusions}

\subsection{Future Work}\label{sec:futurework}
\begin{itemize}
    \item[$\ast$] GeoSPARQL 1.1: to be completed by July, 2021
    \item[$\ast$] GeoSPARQL 1.2: more adventurous extension - late 2021
    \item[$\ast$] GeoSPARQL 2.0: so-far unspecified
\end{itemize}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\end{document}

% Outline
% 
% Section 1
%   History of GeoSPARWL 1.0
% Section 2
%   motivation to update the spec
% Section 3
%   GeoSPARQL 1.1 additions
%       motivation, and expected use, of new spatial functions. In particular, why in GeoSPARQL when aggregations etc. can be performed elsewhere?
%       Spatial Measure
% Section 4
%       new profile presentation
%       new URI regimes etc
% Section 5
%       expected changed use modes

### 2021-03-15 manuscript.tex
as submitted

@@
 \usepackage{cleveref}
+\usepackage{footmisc}
+\usepackage{bookmark}
 
@@
     Nicholas J. Car\inst{1}\orcidID{0000-0002-8742-7730} \and \\
-    Irina Bastrakova\inst{2}
+    Irina Bastrakova\inst{2}\orcidID{0000-0002-4643-7289}
 }
@@
 LocI (Location Index) consists of 7 nationally-significant spatial datasets such as the Australian Statistical Geographies System. 
-LongSpine (Longitudinal Spine of Government Functions) consists of multiple datasets of Australian government structure, such as the 
-Australian Government Organisations Register, as well as vocabularies of government functions. Both projects interpreted existing open 
+LongSpine (Longitudinal Spine of Government Functions) consists of multiple datasets of Australian government structure. Both projects interpreted existing open 
 datasets into Linked Data form and provided online delivery of their the parts as well as infrastructure for their use as a single system.\\
 
-Here described is the Climate and Resilience Services Australia’s Data Identify, Collect and Connect project's next-generation 
-implementation of the ``spines'' patterns and architecture and partial direct reuse of LocI. We discuss: differences with the originals, in particular LocI; original 
-element reuse; and future-proofing steps, technical and non-technical. We also discuss the new expectations placed on this second-generation 
-system, in particular the requirement to work with non-Linked Data spatial data systems, and how this system 
-is pushing spatial and \textit{Semantic Web} standards development such as DGGS and GeoSPARQL.
+Here described is the Climate and Resilience Services Australia’s Data Identify, Collect and Connect project's reuse and extension of LocI. 
+We discuss LocI design, this project's differences and key requirement of this project, in particular the requirement to work with non-Linked Data 
+spatial data systems, and how this system is pushing spatial and \textit{Semantic Web} standards development such as DGGS and GeoSPARQL.
 
-\keywords{Location Index \and LocI \and LongSpine \and GeoSPARQL \and DGGS \and Spatial Data on the Web \and Australia \and data spine \and national data infrastructure}
+\keywords{Location Index \and LocI \and GeoSPARQL \and DGGS \and Spatial Data on the Web \and Australia \and national data infrastructure}
 \end{abstract}
@@
 This paper describes the SW/LD and DGGS approaches being implemented in CaRSA's ``Data Identify, Collect, and Connect'' project that we will 
-refere to as \textit{the project}. The project extends the approach taken by the Location Index project described in the next section.
+refere to as \textit{this project}. The project extends the approach taken by the Location Index project described in the next section.
 
@@
     Australian government \textit{Environment}, \textit{Society} and \textit{Economy} data}
-    \label{fig:geosparql11ontology}
+    \label{fig:loci-brochure}
 \end{figure}
@@
 workers in data analysis using spatial information by providing pre-integrated, authoratitive, spatial datasets that can be used in 
-online, open data scenarios, within secure data integration environments and across the two.
+online, open data scenarios, within secure data integration environments and across the two. The project deals with data from multiple domains,
+see Figure~\ref{fig:loci-brochure}.
 
@@
     \item[$\ast$] federated publication of datasets via standard Linked Data APIs
-    \item[$\ast$] use of VoID \texttt{Linkset}~\cite{alexander_describing_2011} instances to crosswalk datasets
+    \item[$\ast$] use of VoID \texttt{Linkset}~\footnote{\url{https://www.w3.org/TR/void/}} instances to crosswalk datasets
     \begin{itemize}
@@
 
-LocI's initial spatial datasets are from a number of domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
-\footnote{The original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by LocI: \url{http://linked.data.gov.au/dataset/geofabric}}, 
+LocI's datasets are from many domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
+\footnote{Original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by LocI: \url{http://linked.data.gov.au/dataset/geofabric}}, 
 a collection of surface hydrology features), human/census (the \textit{Australian Statistical Geography Standard} spatial areas)
@@
 
-The LocI system's architecture is shown in \ref{fig:loci-arch} for architectural details. It shows the LocI Data Cache, which is a multi-graph triplestore, 
+LocI architecture is shown in Figure~\ref{fig:loci-arch} for architectural details. It shows the LocI Data Cache, which is a multi-graph triplestore, 
 obtains its data by ``pulling'' RDF datasets through APIs that both interpret non-RDF data for online delivery and are also able to create static RDF 
@@
     \centering
-    \includegraphics[width=\linewidth]{images/loci-arch.png}
-    \caption{An informal architecture diagram of the LocI project's \textit{Linked Data} infrastructure.}
+    \includegraphics[width=0.8\linewidth]{images/loci-arch.png}
+    \caption{An informal architecture diagram of LocI's \textit{Linked Data} infrastructure.}
     \label{fig:loci-arch}
@@
 \section{CaRSA Project Changes}\label{sec:changes}
+\subsection{Data Validity}
+This project's datasets are LocI datasets and the project knowledge Graph (KG) is similar to the LocI cache, however conformance to LocI is not easily
+ testable: data reasoning with LocI ontologies can check for incorrect inferences but no contraint language validators are available. This project implements formal \textit{profiles}, which 
+are specifications defining dependencies and validation tooling. This project uses profiles for requirements for data 
+publication by API, dataset suitability for the KG and for use and display by clients and they are defined using 
+\textit{The Profiles Vocabulary}~\cite{atkinson_profiles_2020} and all listed in the project catalogue\footnote{\label{catalogue} \url{https://w3id.org/carsa-loci/catalogue}}.
+
+\subsection{Discrete Global Grid System (DGGS) use}
+LocI aspired to use DGGS geometries\footnote{See the defining \textit{Abstract Specification}~\cite{purss_topic_2017} for indications of potential benefits of 
+DGGS and the more recent \textit{OGC Engineering Report}~\cite{gibb_ogc_2021} for current thinking about how to integrate DGGS use within traditional spatial 
+infrastructure.} but never really did: DGGS data was produced but not really used. This project has produced DGGS versions of all \texttt{Feature} instances' 
+geometries, has stored them alongside traditional geometries within the KG (a triplestore) and has implemented GeoSPARQL~\cite{open2012ogc} functions
+within the triplestore SPARQL extension libraries (Apache Jena's ARC\footnote{\url{https://jena.apache.org/documentation/query/extension.html}}) that work with 
+DGGS geometry representations. These functions are used to obviate the need for LocI's Geometry Data Store and thus reduce infrastructure complexity.
+
+An important enabling factor in this use of DGGS with GeoSPARQL is the inclusion of DGGS geometry serializations within version 1.1 of GeoSPARQL which was motivated
+by LocI project requirements. This version is currently under review and is expected to be published around the time of this paper's publication. Working documents 
+are avalable\footnote{See \url{https://opengeospatial.github.io/ogc-geosparql/} for the GeoSPARQL ``Standards Working Groups`` 's working documents}.
+
+\subsection{Observations data use}
+LocI anticipated observational data - human/industry statistics or natural-world observation data - wuold be used with its spatial data. This project
+implements two such datasets: 1. population data taken from the 2016 Australian census; 2. ``exposure'' data per statistical area - this is data about the vulnerability
+of physical infrastructure to natural hazards.
+This project has developed an ``Observations Dataset'' profile (see the project catalogue \footref{catalogue}) that defines the characteristics of a LocI-comatable
+observations dataset using the profiling mechanisms mentioned above.
+
+\subsection{Knowledge Graph (KG) importing}
+This project's KG includes LocI datasets as well as new LocI-conformant datasets. To avoid duplication, this project intends to import LocI content unchanged however, 
+currently, the additional requirements this project has (see the listed changes above) mean that LocI datasets have to be extended and thus reuse of LocI datasets
+or the data cache (see Figure~\ref{fig:loci-arch}) is not currently possible. For now, a ``LocI 2 KG'' has een created and imported into this project's KG (see 
+\ref{fig:carsa-arch}) but this will be removed when LocI implements this project's elements.
+
+\subsection{Clients and Management}
+LocI implemented some generic and specific clients of its data holdings\footnote(See \url{https://loci.cat/#datasets-and-applications} for a list). This project can reuse 
+some of them, such as \textit{IDer Down}\footnote{\url{https://excelerator.loci.cat/iderdown}} due to the same dataset structures used, however this project has a pair of 
+major objectived that have necessitated different clients. These are:
+
+\begin{enumerate}
+    \item Management of data by versions in the project KG
+    \item Demonstration of the integration of traditional spatial web data display and Linked Data
+\end{enumerate}
+
+For the first, this project has implemented a sophsticated application layer on top of its KG: the \textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}}
+is used to track, select for use, update and generally govern datasets. This results in a new administrative interface that LocI never had since it was not tasked with operational
+data management, only proof-of-concpet system implementation. For the second, information
+flows between a traditional web spatial data portal\footnote{The re-deployable TerriaJS (\url{https://terria.io/}) globe is deployed for this project at \url{https://w3id.org/carsa-loci/globe}}
+and a Linked Data browser\footnote{This system allows for the browsing of content within this project's KG, as opposed to the LD dereferencing of individual resources 
+which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information witin the portal supplied by KG queries. This demonstrated
+LD / SW data for previous implementations of this data portal software just present simple type key / value pairs of information per-\texttt{Feature}.
+
+\subsection{More standardized Dataset APIs}
+LocI implemented LD APIs for spatial datasets that followed standard LD protocols and the data model negotiation protocols of \textit{Content Negotiation by Profile} (ConnegP)~\cite{atkinson_profiles_2020}.
+Content within these APIs was all discoverable since top-level elements - dataset declarations - linked to their content registers and registers linked to individual \texttt{Features}, 
+however no strict or common spatial API structure was used.
+This project implements APIs as both LD APIs and also as \textit{OGC API: Features}~\cite{clemens_portele_ogc_2019} APIs\footnote{See an example of such an API online at \url{https://w3id.org/carsa-loci/provinces} or browse the project catalogue, as linked to in previous footnotes}.
+This is possible due to ConnegP implementations being able to select data models and formats per API endpoint using general mecahnics (HTTP headers or URI query strings) that can be constrained
+to meet OGC API: Features requiements. ConnegP APIs are also used to deliver the Observations datasets but these are not conformant with OGC API:Features since they don't contains any geometry 
+infromation - they link to spatial datasets' \texttt{Features} for their data's spatial information.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{images/carsa-arch.png}
+    \includegraphics[width=0.8\linewidth]{images/carsa-arch.png}
     \caption{An informal architecture diagram of the CaRSA project's \textit{Linked Data} infrastructure}
-    \label{fig:geosparql11ontology}
+    \label{fig:carsa-arch}
 \end{figure}
@@
 \section{Conclusions}\label{sec:conclusions}
+This project is both reuser of LocI systems and an extender of them. Core benefits of spatial Linked Data are preserved - distributed dataset publication, human- and machine-readable 
+web content - and Semantic Web methods - inferencing, ontology modelling however new spatial data indexing is applied (Discrete Global Grid System use), total project data holdings management is
+enabled, data validators created and new clients are delivered.
 
 \subsection{Future Work}\label{sec:futurework}
-\begin{itemize}
-    \item[$\ast$] GeoSPARQL 1.1: to be completed by July, 2021
-    \item[$\ast$] GeoSPARQL 1.2: more adventurous extension - late 2021
-    \item[$\ast$] GeoSPARQL 2.0: so-far unspecified
-\end{itemize}
+This project will operate in test mode until July, 2021, after which time it is expected the system will move to full production. When that happens, this system will be highly dependent on the 
+dependable supply of its datasets to make guarentees about system data currency.
+To ensure this, inter-agency data supply chain management - stated under the precursor LocI project but not completed -
+must be completed.
+
+For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agncies to be able to model datasets using Semantic Web ontologies and to produce Linked Data verisions
+of them for delivery via APIs.
+This will require strong motivation from central government data users to ensure thee requriements are met as implementing these approaches and tools is a socio-technical
+challenge, not purely a technical one.
 

### 2021-03-15 manuscript.tex
updates from Marcus' comments

@@
 
-\subsection{Clients and Management}
-LocI implemented some generic and specific clients of its data holdings\footnote(See \url{https://loci.cat/#datasets-and-applications} for a list). This project can reuse 
-some of them, such as \textit{IDer Down}\footnote{\url{https://excelerator.loci.cat/iderdown}} due to the same dataset structures used, however this project has a pair of 
-major objectived that have necessitated different clients. These are:
+\subsection{Data and metadata management}
+LocI had no requirement to manage the state of the data it coalesced into its cache as such operational management was out of scope for the technical demonstrator. However, this project
+is moving to a production KG that must managed all of its contents to assure currency and so on. For this reason, this project has implemented a sophsticated application layer on top of its KG: the 
+\textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}}, which is used to track, select for use, update and generally govern datasets. This application
+supports provenance absorbtion (for datasets that contain provenance) and provenance generation (for data processing contained within the platform) as well as managed item (dataset, ontology, vocabulary)
+status tracking and even the automated calculation of \textit{FAIR Scores}\footnote{Scored for datasets rated against the \textit{FAIR PRinciples}: \url{https://www.go-fair.org/fair-principles/}}.
 
-\begin{enumerate}
-    \item Management of data by versions in the project KG
-    \item Demonstration of the integration of traditional spatial web data display and Linked Data
-\end{enumerate}
-
-For the first, this project has implemented a sophsticated application layer on top of its KG: the \textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}}
-is used to track, select for use, update and generally govern datasets. This results in a new administrative interface that LocI never had since it was not tasked with operational
-data management, only proof-of-concpet system implementation. For the second, information
+\subsection{Clients}
+LocI implemented some generic and specialised clients of its data holdings\footnote(See \url{https://loci.cat/#datasets-and-applications} for a list). This project can reuse some of them, such as 
+\textit{IDer Down}\footnote{\url{https://excelerator.loci.cat/iderdown}} which is used to download IDs for all instances of a \texttt{Feature} type, due to the same dataset structures being used.
+However, this project is also charged with the demonstration of the integration of traditional spatial web data display and Linked Data. For this reason, information
 flows between a traditional web spatial data portal\footnote{The re-deployable TerriaJS (\url{https://terria.io/}) globe is deployed for this project at \url{https://w3id.org/carsa-loci/globe}}
 and a Linked Data browser\footnote{This system allows for the browsing of content within this project's KG, as opposed to the LD dereferencing of individual resources 
-which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information witin the portal supplied by KG queries. This demonstrated
-LD / SW data for previous implementations of this data portal software just present simple type key / value pairs of information per-\texttt{Feature}.
+which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information accessible witin the portal supplied by KG queries. Previous spatial web data display
+only presents simple type key / value pairs of information per-\texttt{Feature} but this system presents graph data which can be followed. Also, the management requierment, described above, has 
+necessitated an adminstrative interface to this project's KG, that LocI never had.
 
@@
 \section{Conclusions}\label{sec:conclusions}
-This project is both reuser of LocI systems and an extender of them. Core benefits of spatial Linked Data are preserved - distributed dataset publication, human- and machine-readable 
+This project is both reuser of LocI systems and an extender of them. Core benefits of spatial Linked Data are preserved - harmonised use of distributed datasets, human- and machine-readable 
 web content - and Semantic Web methods - inferencing, ontology modelling however new spatial data indexing is applied (Discrete Global Grid System use), total project data holdings management is
-enabled, data validators created and new clients are delivered.
+enabled, data validators created and new clients are delivered. The resulting system is a proto-operational system as opposed to a proof-of-concept.
 

### 2021-03-15 manuscript.tex
further harmonised addition

@@
 relevant to natural disaster management. Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
-standardiseing web service-delivered information and cross-cataloging datasets, but forward-looking methdos are too. In particular,
+standardising web services and cross-cataloging datasets, but forward-looking methdos are too. In particular,
 \textit{Semantic Web} (SW) and \textit{Linked Data} (LD) technologies\footnote{By ``Linked Data'', as opposed to ``linked data'' or ``data linkage'' etc.,
-we mean systems and data that implement a number of \textit{Semantic Web} technologies (RDF, OWL, SKOS, SPARQL, etc.) which are primarily 
-defined as a series of \href{https://www.w3.org/standards/semanticweb/data}{World Wide Web Consortium} (W3C) standards. The W3C's defintion of 
+we mean systems and data that implement a number of \textit{Semantic Web} technologies (RDF, OWL, SKOS, SPARQL, etc.), primarily 
+defined by a series of \href{https://www.w3.org/standards/semanticweb/data}{World Wide Web Consortium} (W3C) standards. The W3C's defintion of 
 \textit{Semantic Web} is that it is a ``Web of Data'', an evolved Internet able to be queried by machineswhich can draw inferences from it.}
-are being used to integrate different, but relativley similar, datasets that are published in a distributed manner and
+are being used to integrate different, but relatively similar, datasets that are published in a distributed manner and
 \textit{Discrete Global Grid System} (DGGS) spatial data methods are being used to integrate spatial data from multiple sources.
 
-This paper describes the SW/LD and DGGS approaches being implemented in CaRSA's ``Data Identify, Collect, and Connect'' project that we will 
+This paper describes the SW/LD and DGGS approaches to publish distributed and harmonised data being implemented in CaRSA's ``Data Identify, Collect, and Connect'' project that we will 
 refere to as \textit{this project}. The project extends the approach taken by the Location Index project described in the next section.

### 2021-03-18 manuscript.tex
changes for Irina and to include CSIRO ref

@@
 
-\title{CaRSA Data Identify, Collect, and Connect: A second-generation, national GeoLD system in Australia}
-\titlerunning{CaRSA LocI}
+\title{L4DR: A 2nd-gen, national GeoLD system}
+\titlerunning{Loc-I for Disaster Recovery}
 
@@
 \begin{abstract}
-In 2018 – 2020, Australia built two \textit{Linked Data} ``spines'' - themed collections of interoperable reference data - called LocI and LongSpine. 
-LocI (Location Index) consists of 7 nationally-significant spatial datasets such as the Australian Statistical Geographies System. 
-LongSpine (Longitudinal Spine of Government Functions) consists of multiple datasets of Australian government structure. Both projects interpreted existing open 
-datasets into Linked Data form and provided online delivery of their the parts as well as infrastructure for their use as a single system.\\
+Increasingly, multiple sources of data are available for disaster recovery planning and emergency service scheduling. Data sharing systems may
+have to simultaneously cover multiple diverse use cases (e.g. social, environmental and economic) and be transparent, verifiable and trusted. 
+The 2020 Australian bushfire crisis and the global COVID-19 pandemic are examples of complex crisis events where lots of data sources are available.\\
 
-Here described is the Climate and Resilience Services Australia’s Data Identify, Collect and Connect project's reuse and extension of LocI. 
-We discuss LocI design, this project's differences and key requirement of this project, in particular the requirement to work with non-Linked Data 
+In 2018 – 2020, Australia built several \textit{Linked Data} ``spines'' - themed collections of interoperable reference data that simplify data 
+integreation in particular domains. 
+The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
+Loc-I delivered Linked Data forms of its datasets and provided infrastructure for their use as a single system.\\
+
+Here described is \textit{Loc-I for Disaster Recorvery}, a scenario deployment of Loc-I.
+We discuss original Loc-I design, this project's differences and its different key requirements, isuch as to integrate Linked Data with traditional
 spatial data systems, and how this system is pushing spatial and \textit{Semantic Web} standards development such as DGGS and GeoSPARQL.
 
-\keywords{Location Index \and LocI \and GeoSPARQL \and DGGS \and Spatial Data on the Web \and Australia \and national data infrastructure}
+\keywords{Location Index \and Loc-I \and GeoSPARQL \and DGGS \and Spatial Data on the Web \and Australia \and national data infrastructure}
 \end{abstract}
@@
 \section{Introduction}\label{sec:introduction}
-\subsection{CaRSA Motivation}
-Climate and Resilience Services Australia (CaRSA) is a new Australia government cross-agency initiative\footnote{``Australia commits to climate resilience'', \url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}
-that will:
+\subsection{Motivation}
+Australia suffers large floods and bushfires, so Australian government is committing substantial resources over 
+multiple years to new cross-agency data sharing initiatives\footnote{``Australia commits to climate resilience'', 
+\url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}
+that will ``connect and leverage the Commonwealth’s extensive climate and natural disaster risk information to further prepare for and build resilience to natural disasters''.
 
-\begin{quote}
-    connect and leverage the Commonwealth’s extensive climate and natural disaster risk information to further prepare for and build 
-    resilience to natural disasters
-\end{quote}
-
-Since Australia is prone to very damaging natural disasters such as bush fires, floods and droughts, this is a major government initiative
-allocated good resourcing and the commitment is for multiple years.
-
-\subsection{CaRSA Demonstrator Projects}
-Several of the demonstrator projects for CaRSA sought to test different ways of combining information from multiple government agencies 
-relevant to natural disaster management. Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
+\subsection{Demonstrator Projects}
+Several of demonstrator projects for an anticipated new data sharing regime were conducted in early 2021. 
+Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
 standardising web services and cross-cataloging datasets, but forward-looking methdos are too. In particular,
@@
 are being used to integrate different, but relatively similar, datasets that are published in a distributed manner and
-\textit{Discrete Global Grid System} (DGGS) spatial data methods are being used to integrate spatial data from multiple sources.
+\textit{Discrete Global Grid System} (DGGS) spatial data methods are being used to integrate spatial data from multiple sources. In 2019-2020, Geoscience Australia tested DGGS data integration
+for information relevant to bushfires which includes burned/burning areas, vegetation cover and demographics.
 
-This paper describes the SW/LD and DGGS approaches to publish distributed and harmonised data being implemented in CaRSA's ``Data Identify, Collect, and Connect'' project that we will 
+This paper describes the SW/LD and DGGS approaches to publish distributed and harmonised data being implemented by a Geoscience Australia (GA) project that we will 
 refere to as \textit{this project}. The project extends the approach taken by the Location Index project described in the next section.
 
-\section{LocI: The Loction Index}\label{sec:loci}
+\section{Loc-I: The Loction Index}\label{sec:loci}
 
@@
     \includegraphics[width=\linewidth]{images/loci-brochure.png}
-    \caption{A project brochure image, from \cite{car_location_2019}, of LocI with respect to
+    \caption{A project brochure image, from \cite{car_location_2019}, of Loc-I with respect to
     Australian government \textit{Environment}, \textit{Society} and \textit{Economy} data}
@@
 
-In 2018 - 2020, Australian spatial data and research agencies implemented a:
+In 2018 - 2020, Australian spatial data and research agencies (\href{https://www.csiro.au}{CSIRO} \& \href{https://www.ga.gov.au}{Geoscience Australia} foring for the \href{https://www.abs.gov.au}{Australian Bureau of Statistics}) implemented a ``national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}''.
 
-\begin{quotation}
-    national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}
-\end{quotation}
-
-This system, known as the Location Index (LocI)~\cite{car_location_2019}, aims to ``better geospatially integrate and analyze data across 
-government portfolios and information domains''. The main use case addressed by LocI's is to greatly reduce the time taken by government 
+This system, known as the Location Index (Loc-I)~\cite{car_location_2019}, aims to ``better geospatially integrate and analyze data across 
+government portfolios and information domains''. The main use case addressed by Loc-I's is to greatly reduce the time taken by government 
 workers in data analysis using spatial information by providing pre-integrated, authoratitive, spatial datasets that can be used in 
 online, open data scenarios, within secure data integration environments and across the two. The project deals with data from multiple domains,
-see Figure~\ref{fig:loci-brochure}.
-
-Some of the interesting aspects of LocI's design include:
+see Figure~\ref{fig:loci-brochure}. Some of the interesting aspects of Loc-I's design include:
 
@@
         \item[$-$] this service extends common use of using GeoSPARQL~\cite{open2012ogc} by storing \texttt{Geometry} instances seperately from the \texttt{Feature} instances they are the geometries for.
-This allows the geometry data to be managed in a PostGIS database~\footnote{\url{https://postgis.net/}}, not a triplestore, as usually used for GeoSPARQL data.
+This allows the geometry data to be managed in a PostGIS database\footnote{\url{https://postgis.net/}}, not a triplestore, as usually used for GeoSPARQL data.
     \end{itemize}
@@
 
-LocI's datasets are from many domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
-\footnote{Original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by LocI: \url{http://linked.data.gov.au/dataset/geofabric}}, 
+Loc-I's datasets are from many domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
+\footnote{Original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by Loc-I: \url{http://linked.data.gov.au/dataset/geofabric}}, 
 a collection of surface hydrology features), human/census (the \textit{Australian Statistical Geography Standard} spatial areas)
@@
 
-LocI architecture is shown in Figure~\ref{fig:loci-arch} for architectural details. It shows the LocI Data Cache, which is a multi-graph triplestore, 
+Loc-I architecture is shown in Figure~\ref{fig:loci-arch} for architectural details. It shows the Loc-I Data Cache, which is a multi-graph triplestore, 
 obtains its data by ``pulling'' RDF datasets through APIs that both interpret non-RDF data for online delivery and are also able to create static RDF 
-versions of the datasets. All LocI datasets conform to the LocI Ontology\footnote{\url{http://linked.data.gov.au/def/loci}} which imports the GeoSPARQL
+versions of the datasets. All Loc-I datasets conform to the Loc-I Ontology\footnote{\url{http://linked.data.gov.au/def/loci}} which imports the GeoSPARQL
 \footnote{\url{http://www.opengis.net/doc/IS/geosparql/1.0}} and DCAT\footnote{\url{https://www.w3.org/TR/2014/REC-vocab-dcat-20140116/}} ontologies. 
@@
     \includegraphics[width=0.8\linewidth]{images/loci-arch.png}
-    \caption{An informal architecture diagram of LocI's \textit{Linked Data} infrastructure.}
+    \caption{An informal architecture diagram of Loc-I's \textit{Linked Data} infrastructure.}
     \label{fig:loci-arch}
@@
 
-\section{CaRSA Project Changes}\label{sec:changes}
+\section{Loc-I for Disaster Recovery}\label{sec:changes}
 \subsection{Data Validity}
-This project's datasets are LocI datasets and the project knowledge Graph (KG) is similar to the LocI cache, however conformance to LocI is not easily
- testable: data reasoning with LocI ontologies can check for incorrect inferences but no contraint language validators are available. This project implements formal \textit{profiles}, which 
+This project's datasets are Loc-I datasets and its Knowledge Graph (KG) is similar to the Loc-I cache, however conformance to Loc-I is not easily
+testable: Loc-I provided no data validators. This project implements formal \textit{profiles}, which 
 are specifications defining dependencies and validation tooling. This project uses profiles for requirements for data 
 publication by API, dataset suitability for the KG and for use and display by clients and they are defined using 
-\textit{The Profiles Vocabulary}~\cite{atkinson_profiles_2020} and all listed in the project catalogue\footnote{\label{catalogue} \url{https://w3id.org/carsa-loci/catalogue}}.
+\textit{The Profiles Vocabulary}~\cite{atkinson_profiles_2020} and all listed in the project's LD catalogue\footnote{\label{catalogue} \url{https://w3id.org/l4dr/explorer}}.
 
 \subsection{Discrete Global Grid System (DGGS) use}
-LocI aspired to use DGGS geometries\footnote{See the defining \textit{Abstract Specification}~\cite{purss_topic_2017} for indications of potential benefits of 
+Loc-I aspired to use DGGS geometries\footnote{See the defining \textit{Abstract Specification}~\cite{purss_topic_2017} for indications of potential benefits of 
 DGGS and the more recent \textit{OGC Engineering Report}~\cite{gibb_ogc_2021} for current thinking about how to integrate DGGS use within traditional spatial 
-infrastructure.} but never really did: DGGS data was produced but not really used. This project has produced DGGS versions of all \texttt{Feature} instances' 
+infrastructure.} but never really did: DGGS data was produced but not used in direct support of Loc-I use. In 2020, Geoscience Australia evaluated DGGS integration of data
+relating to bushfires in Australia - vegeration, population and bush fire extent information and from this established some new DGGS integration methods. Also, SURROUND Australia
+implemented DGGS data delivery via Linked Data APIs for the OGC,s \textit{Testbed 16} interoperability experiment~\cite{gibb_ogc_2021}.
+Using the GA DGGS methods and SURROUND tooling, this project has produced DGGS versions of all \texttt{Feature} instances' 
 geometries, has stored them alongside traditional geometries within the KG (a triplestore) and has implemented GeoSPARQL~\cite{open2012ogc} functions
 within the triplestore SPARQL extension libraries (Apache Jena's ARC\footnote{\url{https://jena.apache.org/documentation/query/extension.html}}) that work with 
-DGGS geometry representations. These functions are used to obviate the need for LocI's Geometry Data Store and thus reduce infrastructure complexity.
+DGGS geometry representations. These functions are used to obviate the need for Loc-I's Geometry Data Store and thus reduce infrastructure complexity.
 
 An important enabling factor in this use of DGGS with GeoSPARQL is the inclusion of DGGS geometry serializations within version 1.1 of GeoSPARQL which was motivated
-by LocI project requirements. This version is currently under review and is expected to be published around the time of this paper's publication. Working documents 
+by Loc-I project requirements. This version is currently under review and is expected to be published around the time of this paper's publication. Working documents 
 are avalable\footnote{See \url{https://opengeospatial.github.io/ogc-geosparql/} for the GeoSPARQL ``Standards Working Groups`` 's working documents}.
@@
 \subsection{Observations data use}
-LocI anticipated observational data - human/industry statistics or natural-world observation data - wuold be used with its spatial data. This project
+Loc-I anticipated observational data - human/industry statistics or natural-world observation data - wuold be used with its spatial data. This project
 implements two such datasets: 1. population data taken from the 2016 Australian census; 2. ``exposure'' data per statistical area - this is data about the vulnerability
 of physical infrastructure to natural hazards.
-This project has developed an ``Observations Dataset'' profile (see the project catalogue \footref{catalogue}) that defines the characteristics of a LocI-comatable
+This project has developed an ``Observations Dataset'' profile (see the project catalogue\footref{catalogue}) that defines the characteristics of a Loc-I-comatable
 observations dataset using the profiling mechanisms mentioned above.
@@
 \subsection{Knowledge Graph (KG) importing}
-This project's KG includes LocI datasets as well as new LocI-conformant datasets. To avoid duplication, this project intends to import LocI content unchanged however, 
-currently, the additional requirements this project has (see the listed changes above) mean that LocI datasets have to be extended and thus reuse of LocI datasets
-or the data cache (see Figure~\ref{fig:loci-arch}) is not currently possible. For now, a ``LocI 2 KG'' has een created and imported into this project's KG (see 
-\ref{fig:carsa-arch}) but this will be removed when LocI implements this project's elements.
+This project's KG includes Loc-I datasets as well as new Loc-I-conformant datasets. To avoid duplication, this project intends to import Loc-I content unchanged however, 
+currently, the additional requirements this project has (see the listed changes above) mean that Loc-I datasets have to be extended and thus reuse of Loc-I datasets
+or the data cache (see Figure~\ref{fig:loci-arch}) is not currently possible. For now, a ``Loc-I 2 KG'' has een created and imported into this project's KG (see 
+\ref{fig:l4dr-arch}) but this will be removed when Loc-I implements this project's elements.
 
 \subsection{Data and metadata management}
-LocI had no requirement to manage the state of the data it coalesced into its cache as such operational management was out of scope for the technical demonstrator. However, this project
-is moving to a production KG that must managed all of its contents to assure currency and so on. For this reason, this project has implemented a sophsticated application layer on top of its KG: the 
-\textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}}, which is used to track, select for use, update and generally govern datasets. This application
-supports provenance absorbtion (for datasets that contain provenance) and provenance generation (for data processing contained within the platform) as well as managed item (dataset, ontology, vocabulary)
+Operational management of data was out of scope for Loc-I as a technical demonstrator, however, this project
+is moving towards a production system that must managed content to assure currency. For this reason, it has implemented a sophsticated application layer on top of its KG, the 
+\textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}},  used to track, select for use, update and overall govern datasets. This application
+supports provenance absorbtion (for datasets that contain provenance) and generation (for data processing contained within the platform) as well as managed item (dataset, ontology, vocabulary)
 status tracking and even the automated calculation of \textit{FAIR Scores}\footnote{Scored for datasets rated against the \textit{FAIR PRinciples}: \url{https://www.go-fair.org/fair-principles/}}.
@@
 \subsection{Clients}
-LocI implemented some generic and specialised clients of its data holdings\footnote(See \url{https://loci.cat/#datasets-and-applications} for a list). This project can reuse some of them, such as 
-\textit{IDer Down}\footnote{\url{https://excelerator.loci.cat/iderdown}} which is used to download IDs for all instances of a \texttt{Feature} type, due to the same dataset structures being used.
-However, this project is also charged with the demonstration of the integration of traditional spatial web data display and Linked Data. For this reason, information
-flows between a traditional web spatial data portal\footnote{The re-deployable TerriaJS (\url{https://terria.io/}) globe is deployed for this project at \url{https://w3id.org/carsa-loci/globe}}
-and a Linked Data browser\footnote{This system allows for the browsing of content within this project's KG, as opposed to the LD dereferencing of individual resources 
-which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information accessible witin the portal supplied by KG queries. Previous spatial web data display
-only presents simple type key / value pairs of information per-\texttt{Feature} but this system presents graph data which can be followed. Also, the management requierment, described above, has 
-necessitated an adminstrative interface to this project's KG, that LocI never had.
+Loc-I implemented some generic and specialised clients for its data holdings\footnote{See \url{https://loci.cat/\#datasets-and-applications} for a list}. This project can reuse some, such as 
+\textit{IDer Down}\footnote{\url{https://excelerator.loci.cat/iderdown}} - used to download IDs for all \texttt{Feature} type instances - due to the same data structures being used.
+However, this project is also charged with demonstrating integration of Linked Data with traditional spatial web data delivery. For this reason, information
+flows between a traditional web globe\footnote{TerriaJS (\url{https://terria.io/}) at \url{https://w3id.org/l4dr/globe}}
+and a Linked Data browser\footnote{This system allows for the browsing of content within this project's KG as \url{https://w3id.org/l4dr/explorer}, as opposed to the LD dereferencing of individual resources
+which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information accessible witin the globe supplied by KG queries. Previous spatial web data display
+only presents simple type key / value pairs of information per-\texttt{Feature} but this system presents graph data which can be followed. Also, the management requirement, described above, has 
+necessitated an adminstrative interface to this project's KG, that Loc-I never had.
 
 \subsection{More standardized Dataset APIs}
-LocI implemented LD APIs for spatial datasets that followed standard LD protocols and the data model negotiation protocols of \textit{Content Negotiation by Profile} (ConnegP)~\cite{atkinson_profiles_2020}.
+Loc-I implemented LD APIs for spatial datasets that followed standard LD protocols and the data model negotiation protocols of \textit{Content Negotiation by Profile} (ConnegP)~\cite{atkinson_profiles_2020}.
 Content within these APIs was all discoverable since top-level elements - dataset declarations - linked to their content registers and registers linked to individual \texttt{Features}, 
 however no strict or common spatial API structure was used.
-This project implements APIs as both LD APIs and also as \textit{OGC API: Features}~\cite{clemens_portele_ogc_2019} APIs\footnote{See an example of such an API online at \url{https://w3id.org/carsa-loci/provinces} or browse the project catalogue, as linked to in previous footnotes}.
+This project implements APIs as both LD APIs and also as \textit{OGC API: Features}~\cite{clemens_portele_ogc_2019} APIs\footnote{See an example of such an API online at \url{https://w3id.org/l4dr/provinces} or browse the project catalogue, as linked to in previous footnotes}.
 This is possible due to ConnegP implementations being able to select data models and formats per API endpoint using general mecahnics (HTTP headers or URI query strings) that can be constrained
-to meet OGC API: Features requiements. ConnegP APIs are also used to deliver the Observations datasets but these are not conformant with OGC API:Features since they don't contains any geometry 
+to meet OGC API: Features requiements. ConnegP APIs are also used to deliver the observations datasets but these are not conformant with OGC API:Features since they don't contains any geometry 
 infromation - they link to spatial datasets' \texttt{Features} for their data's spatial information.
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{images/carsa-arch.png}
-    \caption{An informal architecture diagram of the CaRSA project's \textit{Linked Data} infrastructure}
-    \label{fig:carsa-arch}
+    \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
+    \caption{An informal architecture diagram of the L4DR project's \textit{Linked Data} infrastructure}
+    \label{fig:l4dr-arch}
 \end{figure}
@@
 \section{Conclusions}\label{sec:conclusions}
-This project is both reuser of LocI systems and an extender of them. Core benefits of spatial Linked Data are preserved - harmonised use of distributed datasets, human- and machine-readable 
+This project is both reuser of Loc-I systems and an extender of them. Core benefits of spatial Linked Data are preserved - harmonised use of distributed datasets, human- and machine-readable 
 web content - and Semantic Web methods - inferencing, ontology modelling however new spatial data indexing is applied (Discrete Global Grid System use), total project data holdings management is
@@
 \subsection{Future Work}\label{sec:futurework}
-This project will operate in test mode until July, 2021, after which time it is expected the system will move to full production. When that happens, this system will be highly dependent on the 
-dependable supply of its datasets to make guarentees about system data currency.
-To ensure this, inter-agency data supply chain management - stated under the precursor LocI project but not completed -
-must be completed.
-
-For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agncies to be able to model datasets using Semantic Web ontologies and to produce Linked Data verisions
-of them for delivery via APIs.
-This will require strong motivation from central government data users to ensure thee requriements are met as implementing these approaches and tools is a socio-technical
-challenge, not purely a technical one.
+This project will operate in test mode until July, 2021, the likely, full production, when the system will be highly dependent on 
+uninterrupted data supply guarentee currency. To ensure this, inter-agency data supply chain management - stated in the Loc-I project but not completed - 
+must be finalised. For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agncies to be able to make Semantic Web and Linked Data verisions of their data
+for delivery via APIs. This will require strong motivation from central government data users to ensure these requriements are met as implementation is a socio-technical challenge, not purely a 
+technical one.
 

### 2021-03-18 manuscript.tex
Update manuscript.tex
Many grammar and spelling errors

@@
 integreation in particular domains. 
-The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
-Loc-I delivered Linked Data forms of its datasets and provided infrastructure for their use as a single system.\\
+The spatial data spine, Loc-I (Location Index), initially consisted of three nationally-significant spatial datasets, such as the \textit{Australian Statistical Geography Standard}. 
+Loc-I delivers Linked Data forms of its datasets and provided infrastructure for their use as a single system.\\
 
-Here described is \textit{Loc-I for Disaster Recorvery}, a scenario deployment of Loc-I.
+Here we describe \textit{Loc-I for Disaster Recovery}, a scenario deployment extension for Loc-I.
 We discuss original Loc-I design, this project's differences and its different key requirements, isuch as to integrate Linked Data with traditional
@@
 \subsection{Motivation}
-Australia suffers large floods and bushfires, so Australian government is committing substantial resources over 
+Australia suffers large floods and bushfires, so the Australian government is committing substantial resources over 
 multiple years to new cross-agency data sharing initiatives\footnote{``Australia commits to climate resilience'', 
-\url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}
-that will ``connect and leverage the Commonwealth’s extensive climate and natural disaster risk information to further prepare for and build resilience to natural disasters''.
+\url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}, 
+which will ``connect and leverage the Commonwealth’s extensive climate and natural disaster risk information to further prepare for and build resilience to natural disasters''.
 
 \subsection{Demonstrator Projects}
-Several of demonstrator projects for an anticipated new data sharing regime were conducted in early 2021. 
+Several demonstrator projects for an anticipated new data sharing regime were conducted in early 2021. 
 Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
-standardising web services and cross-cataloging datasets, but forward-looking methdos are too. In particular,
+standardising web services and cross-cataloging datasets, and also forward-looking methods. In particular,
 \textit{Semantic Web} (SW) and \textit{Linked Data} (LD) technologies\footnote{By ``Linked Data'', as opposed to ``linked data'' or ``data linkage'' etc.,
@@
 are being used to integrate different, but relatively similar, datasets that are published in a distributed manner and
-\textit{Discrete Global Grid System} (DGGS) spatial data methods are being used to integrate spatial data from multiple sources. In 2019-2020, Geoscience Australia tested DGGS data integration
+spatial data methods using a \textit{Discrete Global Grid System} (DGGS) are being used to integrate spatial data from multiple sources. In 2019-2020, Geoscience Australia tested DGGS data integration
 for information relevant to bushfires which includes burned/burning areas, vegetation cover and demographics.
@@
 
-\section{Loc-I: The Loction Index}\label{sec:loci}
+\section{Loc-I: The Location Index}\label{sec:loci}
 
@@
 
-In 2018 - 2020, Australian spatial data and research agencies (\href{https://www.csiro.au}{CSIRO} \& \href{https://www.ga.gov.au}{Geoscience Australia} foring for the \href{https://www.abs.gov.au}{Australian Bureau of Statistics}) implemented a ``national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}''.
+In 2018 - 2020, Australian spatial data and research agencies (\href{https://www.csiro.au}{CSIRO} \& \href{https://www.ga.gov.au}{Geoscience Australia} **foring** for the \href{https://www.abs.gov.au}{Australian Bureau of Statistics}) implemented a ``national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}''.
 
 This system, known as the Location Index (Loc-I)~\cite{car_location_2019}, aims to ``better geospatially integrate and analyze data across 
-government portfolios and information domains''. The main use case addressed by Loc-I's is to greatly reduce the time taken by government 
+government portfolios and information domains''. The main use case addressed by Loc-I is to greatly reduce the time taken by government 
 workers in data analysis using spatial information by providing pre-integrated, authoratitive, spatial datasets that can be used in 
 online, open data scenarios, within secure data integration environments and across the two. The project deals with data from multiple domains,
-see Figure~\ref{fig:loci-brochure}. Some of the interesting aspects of Loc-I's design include:
+see Figure~\ref{fig:loci-brochure}. Some of the interesting aspects of the Loc-I design include:
 
@@
 
-Loc-I's datasets are from many domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
+The Loc-I datasets are from many domains including environmental (the \textit{Australian Hydrological Geospatial Fabric}
 \footnote{Original, non-RDF dataset: \url{http://www.bom.gov.au/water/geofabric/}, and the online LD version implemented by Loc-I: \url{http://linked.data.gov.au/dataset/geofabric}}, 
@@
 
-Loc-I architecture is shown in Figure~\ref{fig:loci-arch} for architectural details. It shows the Loc-I Data Cache, which is a multi-graph triplestore, 
+Some details of the Loc-I architectureares shown in Figure~\ref{fig:loci-arch}. It shows the Loc-I Data Cache, which is a multi-graph triplestore, 
 obtains its data by ``pulling'' RDF datasets through APIs that both interpret non-RDF data for online delivery and are also able to create static RDF 
@@
 \subsection{Data Validity}
-This project's datasets are Loc-I datasets and its Knowledge Graph (KG) is similar to the Loc-I cache, however conformance to Loc-I is not easily
+The project datasets are Loc-I datasets and its Knowledge Graph (KG) is similar to the Loc-I cache, however conformance to Loc-I is not easily
 testable: Loc-I provided no data validators. This project implements formal \textit{profiles}, which 
@@
 
-\subsection{Discrete Global Grid System (DGGS) use}
-Loc-I aspired to use DGGS geometries\footnote{See the defining \textit{Abstract Specification}~\cite{purss_topic_2017} for indications of potential benefits of 
+\subsection{Use of Discrete Global Grid System (DGGS)}
+It was planned for Loc-I to use DGGS geometries\footnote{See the defining \textit{Abstract Specification}~\cite{purss_topic_2017} for indications of potential benefits of 
 DGGS and the more recent \textit{OGC Engineering Report}~\cite{gibb_ogc_2021} for current thinking about how to integrate DGGS use within traditional spatial 
-infrastructure.} but never really did: DGGS data was produced but not used in direct support of Loc-I use. In 2020, Geoscience Australia evaluated DGGS integration of data
+infrastructure.} but this has not yet been integrated into the core Loc-I cache. In 2020, Geoscience Australia evaluated DGGS integration of data
 relating to bushfires in Australia - vegeration, population and bush fire extent information and from this established some new DGGS integration methods. Also, SURROUND Australia
@@
 by Loc-I project requirements. This version is currently under review and is expected to be published around the time of this paper's publication. Working documents 
-are avalable\footnote{See \url{https://opengeospatial.github.io/ogc-geosparql/} for the GeoSPARQL ``Standards Working Groups`` 's working documents}.
+are available\footnote{See \url{https://opengeospatial.github.io/ogc-geosparql/} for the GeoSPARQL ``Standards Working Groups`` 's working documents}.
 
@@
 of physical infrastructure to natural hazards.
-This project has developed an ``Observations Dataset'' profile (see the project catalogue\footref{catalogue}) that defines the characteristics of a Loc-I-comatable
+This project has developed an ``Observations Dataset'' profile (see the project catalogue\footref{catalogue}) that defines the characteristics of a Loc-I-compatible (conformant?)
 observations dataset using the profiling mechanisms mentioned above.
@@
 \subsection{Knowledge Graph (KG) importing}
-This project's KG includes Loc-I datasets as well as new Loc-I-conformant datasets. To avoid duplication, this project intends to import Loc-I content unchanged however, 
+This project's KG includes Loc-I datasets as well as new Loc-I-conformant (compatible?) datasets. To avoid duplication, this project intends to import Loc-I content unchanged however, 
 currently, the additional requirements this project has (see the listed changes above) mean that Loc-I datasets have to be extended and thus reuse of Loc-I datasets
@@
 \section{Conclusions}\label{sec:conclusions}
-This project is both reuser of Loc-I systems and an extender of them. Core benefits of spatial Linked Data are preserved - harmonised use of distributed datasets, human- and machine-readable 
+This project is both re-user and extender of Loc-I systems. Core benefits of spatial Linked Data are preserved - harmonised use of distributed datasets, human- and machine-readable 
 web content - and Semantic Web methods - inferencing, ontology modelling however new spatial data indexing is applied (Discrete Global Grid System use), total project data holdings management is
@@
 \subsection{Future Work}\label{sec:futurework}
-This project will operate in test mode until July, 2021, the likely, full production, when the system will be highly dependent on 
+This project will operate in test mode until July 2021. Full production will be highly dependent on 
 uninterrupted data supply guarentee currency. To ensure this, inter-agency data supply chain management - stated in the Loc-I project but not completed - 
 must be finalised. For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agncies to be able to make Semantic Web and Linked Data verisions of their data
-for delivery via APIs. This will require strong motivation from central government data users to ensure these requriements are met as implementation is a socio-technical challenge, not purely a 
+for delivery via APIs. This will require strong motivation from central government data users to ensure these requirements are met as implementation is a socio-technical challenge, not purely a 
 technical one.

### 2021-04-22 manuscript.tex
review changes

--- 2021-03-18 manuscript.tex
@@
 \institute{
-    {
-    SURROUND Australia Pty Ltd., Australia \&\\
+    {SURROUND Australia Pty Ltd., Australia \&\\
     Australian National University, Australia\\
@@
     \and
-    {
-        Geoscience Australia\\
-        \email{irina.bastrakova@ga.gov.au}
-    }
+    {Geoscience Australia\\
+    \email{irina.bastrakova@ga.gov.au}}
 }
@@
 In 2018 – 2020, Australia built several \textit{Linked Data} ``spines'' - themed collections of interoperable reference data that simplify data 
-integreation in particular domains. 
+integration in particular domains. 
 The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
@@
 
-Here described is \textit{Loc-I for Disaster Recorvery}, a scenario deployment of Loc-I.
-We discuss original Loc-I design, this project's differences and its different key requirements, isuch as to integrate Linked Data with traditional
-spatial data systems, and how this system is pushing spatial and \textit{Semantic Web} standards development such as DGGS and GeoSPARQL.
+Here described is \textit{Loc-I for Disaster Recovery}, a scenario deployment of Loc-I.
+We discuss original Loc-I design, this project's key requirements and other differences, such as integrating with traditional
+spatial data systems, and how this system is pushing the development of spatial and \textit{Semantic Web} standards, such as DGGS and GeoSPARQL.
 
@@
 Australia suffers large floods and bushfires, so Australian government is committing substantial resources over 
-multiple years to new cross-agency data sharing initiatives\footnote{``Australia commits to climate resilience'', 
+multiple years to new cross-agency data sharing initi-atives\footnote{``Australia commits to climate resilience'', 
 \url{https://minister.awe.gov.au/ley/media-releases/australia-commits-climate-resilience}}
@@
 Traditional methods of data aggregation are being tested, such as data pooling in shared facilities,
-standardising web services and cross-cataloging datasets, but forward-looking methdos are too. In particular,
+standardising web services and cross-cataloging datasets, but forward-looking methods are too. In particular,
 \textit{Semantic Web} (SW) and \textit{Linked Data} (LD) technologies\footnote{By ``Linked Data'', as opposed to ``linked data'' or ``data linkage'' etc.,
 we mean systems and data that implement a number of \textit{Semantic Web} technologies (RDF, OWL, SKOS, SPARQL, etc.), primarily 
-defined by a series of \href{https://www.w3.org/standards/semanticweb/data}{World Wide Web Consortium} (W3C) standards. The W3C's defintion of 
-\textit{Semantic Web} is that it is a ``Web of Data'', an evolved Internet able to be queried by machineswhich can draw inferences from it.}
+defined by a series of \href{https://www.w3.org/standards/semanticweb/data}{World Wide Web Consortium} (W3C) standards. The W3C's definition of 
+\textit{Semantic Web} is that it is a ``Web of Data'', an evolved Internet able to be queried by machines which can draw inferences from it.}
 are being used to integrate different, but relatively similar, datasets that are published in a distributed manner and
@@
 This paper describes the SW/LD and DGGS approaches to publish distributed and harmonised data being implemented by a Geoscience Australia (GA) project that we will 
-refere to as \textit{this project}. The project extends the approach taken by the Location Index project described in the next section.
+refer to as \textit{this project}. The project extends the approach taken by the Location Index project described in the next section.
 
-\section{Loc-I: The Loction Index}\label{sec:loci}
+\section{Loc-I: The Location Index}\label{sec:loci}
 
@@
 In 2018 - 2020, Australian spatial data and research agencies (\href{https://www.csiro.au}{CSIRO} \& \href{https://www.ga.gov.au}{Geoscience Australia} foring for the \href{https://www.abs.gov.au}{Australian Bureau of Statistics}) implemented a ``national and authoritative, also federated, index for Australian spatial data using Semantic Web technologies~\cite{car_location_2019}''.
-
 This system, known as the Location Index (Loc-I)~\cite{car_location_2019}, aims to ``better geospatially integrate and analyze data across 
 government portfolios and information domains''. The main use case addressed by Loc-I's is to greatly reduce the time taken by government 
-workers in data analysis using spatial information by providing pre-integrated, authoratitive, spatial datasets that can be used in 
+workers in data analysis using spatial information by providing pre-integrated, authoritative, spatial datasets that can be used in 
 online, open data scenarios, within secure data integration environments and across the two. The project deals with data from multiple domains,
@@
     \begin{itemize}
-        \item[$-$] these are independently-selectable for use meaning that a specific ccrosswalk, of potentially many, may be selected for use
+        \item[$-$] these are independently-selectable for use meaning that a specific crosswalk, of potentially many, may be selected for use
     \end{itemize} 
@@
     \begin{itemize}
-        \item[$-$] this service extends common use of using GeoSPARQL~\cite{open2012ogc} by storing \texttt{Geometry} instances seperately from the \texttt{Feature} instances they are the geometries for.
+        \item[$-$] this service extends common use of using GeoSPARQL~\cite{open2012ogc} by storing \texttt{Geometry} instances separately from the \texttt{Feature} instances they are the geometries for.
 This allows the geometry data to be managed in a PostGIS database\footnote{\url{https://postgis.net/}}, not a triplestore, as usually used for GeoSPARQL data.
@@
 obtains its data by ``pulling'' RDF datasets through APIs that both interpret non-RDF data for online delivery and are also able to create static RDF 
-versions of the datasets. All Loc-I datasets conform to the Loc-I Ontology\footnote{\url{http://linked.data.gov.au/def/loci}} which imports the GeoSPARQL
-\footnote{\url{http://www.opengis.net/doc/IS/geosparql/1.0}} and DCAT\footnote{\url{https://www.w3.org/TR/2014/REC-vocab-dcat-20140116/}} ontologies. 
+versions of the datasets.
+All Loc-I datasets conform to the Loc-I Ontology\footnote{\url{http://linked.data.gov.au/def/loci}} which imports the GeoSPARQL\footnote{\url{http://www.opengis.net/doc/IS/geosparql/1.0}} and DCAT\footnote{\url{https://www.w3.org/TR/2014/REC-vocab-dcat-20140116/}} ontologies.
 Alongside the Cache is a traditional spatial DB - PostGIS\footnote{\url{https://postgis.net/}} used to perform fast geometry intersections.
@@
 are specifications defining dependencies and validation tooling. This project uses profiles for requirements for data 
-publication by API, dataset suitability for the KG and for use and display by clients and they are defined using 
-\textit{The Profiles Vocabulary}~\cite{atkinson_profiles_2020} and all listed in the project's LD catalogue\footnote{\label{catalogue} \url{https://w3id.org/l4dr/explorer}}.
+publication by API, dataset suitability for the KG and for use and display by clients. It uses ``profiles'' as defined using 
+\textit{The Profiles Vocabulary}~\cite{atkinson_profiles_2020} and all listed in the project's LD catalogue\footnote{\label{catalogue}\url{https://w3id.org/l4dr/explorer}}.
 
@@
 \subsection{Observations data use}
-Loc-I anticipated observational data - human/industry statistics or natural-world observation data - wuold be used with its spatial data. This project
+Loc-I anticipated observational data - human/industry statistics or natural-world observation data - would be used with its spatial data. This project
 implements two such datasets: 1. population data taken from the 2016 Australian census; 2. ``exposure'' data per statistical area - this is data about the vulnerability
@@
 \subsection{Knowledge Graph (KG) importing}
-This project's KG includes Loc-I datasets as well as new Loc-I-conformant datasets. To avoid duplication, this project intends to import Loc-I content unchanged however, 
-currently, the additional requirements this project has (see the listed changes above) mean that Loc-I datasets have to be extended and thus reuse of Loc-I datasets
-or the data cache (see Figure~\ref{fig:loci-arch}) is not currently possible. For now, a ``Loc-I 2 KG'' has een created and imported into this project's KG (see 
-\ref{fig:l4dr-arch}) but this will be removed when Loc-I implements this project's elements.
+This project's KG includes Loc-I datasets as well as new Loc-I-conformant datasets. To avoid duplication, it intends to import Loc-I content unchanged however, 
+currently, the additional requirements this project has (see below) mean that Loc-I datasets hmust be extended and thus reuse of Loc-I datasets
+or the data cache (see Figure~\ref{fig:loci-arch}) is not possible. For now, a ``Loc-I 2 KG'' has een created and imported into this project's KG (see 
+Figure~\ref{fig:l4dr-arch}) but this will be removed when Loc-I implements this project's elements.
 
 \subsection{Data and metadata management}
-Operational management of data was out of scope for Loc-I as a technical demonstrator, however, this project
-is moving towards a production system that must managed content to assure currency. For this reason, it has implemented a sophsticated application layer on top of its KG, the 
+Operational management of data was out of scope for Loc-I as a technical demonstrator only so, its data was mostly un-governed in the project: individual researchers loaded datasets into the Loc-I Cache \textit{ad-hoc}.
+This project has a strong requirement to demonstrate on-going operations and will continuously
+absorb new and updated data, so it has a strong requrement to manage content to assure currency and sustainable growth.
+For this reason, it has implemented a sophisticated application layer on top of its KG, the
 \textit{SURROUND Ontology Platform}\footnote{\url{https://surroundaustralia.com/sop}}, used to track, select for use, update and overall govern datasets. This application
 supports provenance absorbtion (for datasets that contain provenance) and generation (for data processing contained within the platform) as well as managed item (dataset, ontology, vocabulary)
-status tracking and even the automated calculation of \textit{FAIR Scores}\footnote{Scored for datasets rated against the \textit{FAIR PRinciples}: \url{https://www.go-fair.org/fair-principles/}}.
+status tracking for over 20 classes of seamntic asset.
+These classes include TBox items such as ontologies and vocabularies, as well as ABox datasets but also specialised forms of these asset classes, such as \textit{Linksets} (datasets that crosswalk others) and \textit{Profiles} that are TBox objects that use and contrain, but don't defin other TBox assets.
+The platform can also runs workflows for repetative data absorbtion (pulling non-RDF data from source locations, converting it to RDF and presenting it) and also run other calculations on top of data, such as \textit{FAIR Score}\footnote{Scored for datasets rated against the \textit{FAIR PRinciples}: \url{https://www.go-fair.org/fair-principles/}} rating.
 
@@
 flows between a traditional web globe\footnote{TerriaJS (\url{https://terria.io/}) at \url{https://w3id.org/l4dr/globe}}
-and a Linked Data browser\footnote{This system allows for the browsing of content within this project's KG as \url{https://w3id.org/l4dr/explorer}, as opposed to the LD dereferencing of individual resources
-which is acomplished by the APIs implemented for each dataset.} with panels of per-\texttt{Feature} information accessible witin the globe supplied by KG queries. Previous spatial web data display
+and a Linked Data browser\footnote{\url{https://w3id.org/l4dr/explorer}. Allows for browsing of content in project's KG, as opposed to LD dereferencing of resources 
+accomplished by dataset APIs.} with panels of per-\texttt{Feature} information accessible within the globe supplied by KG queries. Previous spatial web data display
 only presents simple type key / value pairs of information per-\texttt{Feature} but this system presents graph data which can be followed. Also, the management requirement, described above, has 
@@
 This is possible due to ConnegP implementations being able to select data models and formats per API endpoint using general mecahnics (HTTP headers or URI query strings) that can be constrained
-to meet OGC API: Features requiements. ConnegP APIs are also used to deliver the observations datasets but these are not conformant with OGC API:Features since they don't contains any geometry 
-infromation - they link to spatial datasets' \texttt{Features} for their data's spatial information.
+to meet OGC API: Features requirements. ConnegP APIs are also used to deliver the observations datasets but these are not conformant with OGC API:Features since they don't contains any geometry 
+information - they link to spatial datasets' \texttt{Features} for their data's spatial information.
 
@@
 uninterrupted data supply guarentee currency. To ensure this, inter-agency data supply chain management - stated in the Loc-I project but not completed - 
-must be finalised. For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agncies to be able to make Semantic Web and Linked Data verisions of their data
-for delivery via APIs. This will require strong motivation from central government data users to ensure these requriements are met as implementation is a socio-technical challenge, not purely a 
+must be finalised. For data to be delivered by owner agencies as Linked Data, assistance will need to be given to those agencies to be able to make Semantic Web and Linked Data versions of their data
+for delivery via APIs. This will require strong motivation from central government data users to ensure these requirements are met as implementation is a socio-technical challenge, not purely a 
 technical one.
@@
 \end{document}
-
-% Outline
-% 
-% Section 1
-%   History of GeoSPARWL 1.0
-% Section 2
-%   motivation to update the spec
-% Section 3
-%   GeoSPARQL 1.1 additions
-%       motivation, and expected use, of new spatial functions. In particular, why in GeoSPARQL when aggregations etc. can be performed elsewhere?
-%       Spatial Measure
-% Section 4
-%       new profile presentation
-%       new URI regimes etc
-% Section 5
-%       expected changed use modes

### 2021-08-20 manuscript.tex
copyright notice

@@
 \usepackage{bookmark}
+\usepackage{tikz}
 
@@
 
+\newcommand\copyrighttext{%
+  \footnotesize Copyright ©2021 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
+\newcommand\copyrightnotice{%
+\begin{tikzpicture}[remember picture,overlay]
+\node[anchor=south,yshift=10pt] at (current page.south) {\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\copyrighttext}}};
+\end{tikzpicture}%
+}
+
 \begin{document}
 
-\title{L4DR: A 2nd-gen, national GeoLD system}
+\title{LDR: A 2nd-gen, National GeoLD System}
 \titlerunning{Loc-I for Disaster Recovery}
@@
 \maketitle
+
+\copyrightnotice
 
@@
     \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
-    \caption{An informal architecture diagram of the L4DR project's \textit{Linked Data} infrastructure}
+    \caption{An informal architecture diagram of the LDR project's \textit{Linked Data} infrastructure}
     \label{fig:l4dr-arch}

### 2021-08-23 manuscript.tex
preparation for publication

--- 2021-04-22 manuscript.tex
@@
 
-\title{L4DR: A 2nd-gen, national GeoLD system}
+\title{LDR: A 2nd-gen, National GeoLD System}
 \titlerunning{Loc-I for Disaster Recovery}
@@
     Irina Bastrakova\inst{2}\orcidID{0000-0002-4643-7289}
+    \thanks{Copyright ©2021 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
 }
@@
 \begin{abstract} 
-Increasingly, multiple sources of data are available for disaster recovery planning and emergency service scheduling. Data sharing systems may
-have to simultaneously cover multiple diverse use cases (e.g. social, environmental and economic) and be transparent, verifiable and trusted. 
-The 2020 Australian bushfire crisis and the global COVID-19 pandemic are examples of complex crisis events where lots of data sources are available.\\
-
+The 2020 Australian bushfire crisis and the global COVID-19 pandemic are examples of complex crisis events where the use of data from multiple sources was sought.
 In 2018 – 2020, Australia built several \textit{Linked Data} ``spines'' - themed collections of interoperable reference data that simplify data
-integration in particular domains. 
+integration from multiple sources in particular domains. 
 The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
-    \caption{An informal architecture diagram of the L4DR project's \textit{Linked Data} infrastructure}
+    \includegraphics[width=0.5\linewidth]{images/l4dr-arch.png}
+    \caption{An informal architecture diagram of the LDR project's \textit{Linked Data} infrastructure}
     \label{fig:l4dr-arch}
